---
title: "Exercise 1 · Body mass index"

---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Data set

The goal of this exercise is to provide a very common and simple case
of twin data analysis using the `mglm4twin` package. In order, to help
you get familiar with the package, we designed a set of step where
you can fill the `???` with your choices and run a model.

The example regards a fairly common continuous trait analysis. 
The dataset is part of the `twinbmi`dataset from the `mets`package.
In this exercise, we restrict our attention to a subset of the original 
data set where we have paired observation for both twin. 
The resulting dataset consists of 4271 (2788 DZ and 1483 MZ) twin-pairs.
The analysis goal is to investigate the genetic and common environment
influences on the body mass index (BMI). We have three covariates available:
`age`, `gender` and `Group`.

```{r}
library(mglm4twin)
data(bmi)
head(bmi)
```

## Exploratory data analysis

Provide some exploratory analyses to show (if any) the correlation
between twin pair concerning the trait body mass index. It is important
to show the difference between MZ and DZ twin. You can use plots and
numeric summaries like the Pearson correlation.

## Model specification

Remember the model specification is done in three steps:

   1. Specifying the linear predictor (mean model).
   2. Specifying the matrix linear predictor (twin dependence structure).
   3. Specifying link and variance function suitable to be response variable type.

Some question to help you to think about each part of the model.

   1. How would you specify the linear predictor for the trait body mass index?
   2. How would you specify the matrix predictor for the trait body mass index? 
   Try to create a sequence of increasing complex models and check the difference 
   between them.
   3. Which link and variance functions are suitable for this case?


### Specyfing the linear predictor

```{r, eval = FALSE}
linear_pred <- ???
```

### Specyfing the matrix linear predictor

```{r, eval = FALSE}
??? = mt_twin(N_DZ = ??, N_MZ = ??, n_resp = ?, model = "??")
??? = mt_twin(N_DZ = ??, N_MZ = ??, n_resp = ?, model = "??")
```


### Specyfing link and variance functions

```{r, eval = FALSE}
link = "???"
variance = "???"
```

## Model fitting


```{r, eval = FALSE}
fit <- mglm4twin(linear_pred = c(??),
                 link = link,
                 variance = variance,
                 matrix_pred = ???, data = bmi)

```

## Model output


```{r, eval = FALSE}
summary(fit, model = "???", biometric = TRUE)

```

